\LARGE \bf When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting

### 2014-12-12 main.tex
R5 LfD physical skills similarity concerns

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
but also contexts such as logic puzzles~\cite{Leyzberg2014} and in music 
classes~\cite{Han2009}.
Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
investigating how humans can instead teach robots (language \cite{Saunders2010} or 
table tennis \cite{Mulling2013}, for example) focuses on the robot's
benefits rather than the learning experienced by the human tutor. Our
work concentrates on this latter aspect.

>>>>

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
but also applications such as logic puzzles~\cite{Leyzberg2014}, in music 
classes~\cite{Han2009}, and physical skills such as caligraphy \cite{Matsui2013}.
Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
investigating how humans can instead teach robots (language \cite{Saunders2010} or 
table tennis \cite{Mulling2013}, for example) focuses on the robot's
benefits rather than the learning experienced by the human tutor. Our
work concentrates on this latter aspect. We note that our work differs from those
where a robot develops physical skills through `learning 
from demonstration' from humans, as the agent we present is only simulating 
fine motor skills for interaction purposes.
